%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage[dvipsnames]{xcolor}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LAST UPDATED DATE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Gloria}{Anholt}
{
	\location{}
	%\vspace{\topsep}
	\begin{center}
	Full stack developer with a demonstrated ability to dive deep into the inner workings of a problem. \\
	I specialize in breaking complex topics down into meaningful, understandable bits. \\
	I love puzzling out how things work by jumping right into the docs and the code.
	\end{center}
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.71\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{3mm}
\section{Tech Experience}

\runsubsection{Bootcamp Teaching Asst (Full-Stack JS)}
\vspace{0.6mm}
\location{ \href{http://www.codefellowspdx.com/}{\textcolor{blue}{Link}} | \href{https://github.com/cfpdx-401d5}{\textcolor{blue}{Code Reviews}}}
Provide mentoring and code reviews for Advanced students at Code Fellows PDX.
\vspace{4.5mm} % Hacky fix - this needs more vertical space than the other two projects for no apparent reason
\begin{tightemize}
\item Topics include Node.js (http/TCP, CLI, file systems), Express.js, MongoDB and 
Mongoose, testing with Mocha and Jest, and React.js with Router and Redux. \\
\end{tightemize}
\sectionsep
\vspace{2mm}

\runsubsection{Transplantr (React)}
\vspace{0.6mm}
\location{ \href{https://transplantr.herokuapp.com/}{\textcolor{blue}{Link}} | \href{https://github.com/GloriaAnholt/React-Transplantr}{\textcolor{blue}{Source Code}}}
An app that lets you compare your current income and economic strength to how much you
would need to make to maintain your current purchasing or renting power in a new city.
\vspace{1.5mm}
\begin{tightemize}
\item Uses US Census, Zillow, and median rental price data, via AJAX calls to APIs.
\item Rewritten using React component architecture with Router and an Express backend.
\item Originally written as a 4-person team using JQuery and Handlebars for templating. \\
End-to-end tested with Mocha. Deployed on Heroku.\\
\end{tightemize}
\sectionsep
\vspace{2mm}

\runsubsection{TechFolio (Angular)}
\vspace{0.6mm}
\location{ \href{https://techfolio.herokuapp.com/}{\textcolor{blue}{Link}} | \href{https://github.com/devfolio/techfolio}{\textcolor{blue}{Source Code}}}
In a one-week sprint, a team of four wrote, tested, and deployed an app which uses OAuth
to link accounts with your GitHub and LinkedIn to dynamically generate a tech portfolio
page.
\vspace{1.5mm} % Hacky fix - this needs more vertical space than the other two projects for no apparent reason
\begin{tightemize}
\item Backend built using the JavaScript MEAN-stack. Data API uses JSON web tokens \\
for
auth, and OAuth API calls to GitHub and LinkedIn.
\item Angular 1 frontend using UI-Router, component-based architecture, and services. \\
\end{tightemize}
\sectionsep
\vspace{2mm}


\runsubsection{Mozilla Marionette (JS)}
\vspace{0.6mm}
\location{ \href{https://hg.mozilla.org/mozilla-central/log?rev=Bug+1256996}{\textcolor{blue}{ Bugzilla: Bug 1256996}}}
Cloned Mozilla Central repository via Mercurial, landed patch in Mozilla Marionette.
\vspace{1.5mm}
\begin{tightemize}
\item Resolved issue in Bugzilla under the mentorship of Maja Frydrychowicz (:maja\_zf).
\end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% PUT TITLES FIRST, company secnd
% remove months from the dates
% add Hope Services work
% aim for a quick skim job by recruiters
% remove adjectives from ILG

\section{Recent Work Experience}
\runsubsection{Instructional Designer} \\
%\descript{}
\vspace{.6mm}
\location{2014 – 2016 | Idea Learning Group Portland, OR}
\vspace{.6mm}
Crafted instructional materials with engaging interactions and elegant clean designs. \\
Completed engineering, safety training, financial, and HR related trainings.
\vspace{.8mm}
\begin{tightemize}
\item Implemented an entire multisystem training course for a billion dollar off-shore
German wind farm. Used engineering technical documents and schematics to \\
create classroom-based training materials (presentation and student handbooks).
\end{tightemize}
\sectionsep
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\runsubsection{EAPSI Summer Fellow} \\
%\descript{}
\vspace{.6mm}
\location{2013 | NSF \& JSPS Tokyo, Japan}
\vspace{.6mm}
Represented United States as "Science Liason" for the National Science Foundation (NSF). \\
\vspace{.5mm}
\begin{tightemize}
\item Worked collaboratively with Japanese researchers through their national \\
science organization, Japanese Society for the Promotion of Science (JSPS).
\end{tightemize}
\sectionsep
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\runsubsection{Teaching Associate, History Dept.} \\
%\descript{}
\vspace{.6mm}
\location{2008 – 2013 | UCLA Los Angeles, CA}
\vspace{.6mm}
Taught intro History of Science, Southeast and East Asian History courses. \\
\vspace{.5mm}
\begin{tightemize}
\item Using 'Socratic' interactive sections, demonstrated critical reading of historical
sources, and taught analytical writing techniques to advanced undergraduates.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.26\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{3mm}
\section{Connect}
Web/ \urlstyle{same}\href{http://www.GloriaAnholt.com}{\textbf{\textcolor{blue}{GloriaAnholt.com}}} \\
Email/ \href{mailto:gloriaanholt@gmail.com}{\textbf{\textcolor{blue}{GloriaAnholt@gmail.com}}} \\
Github/ \href{https://github.com/GloriaAnholt}{\textbf{\textcolor{blue}{GloriaAnholt}}} \\
LinkedIn/ \href{https://www.linkedin.com/in/gloriaanholt}{\textbf{\textcolor{blue}{GloriaAnholt}}} \\
Twitter/ \href{https://twitter.com/totallygloria}{\textbf{\textcolor{blue}{@totallygloria}}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\runsubsection{Programming}
\location{}
Python  \\
JavaScript / ES6 \\
Node / Express \\
React / Router / Redux \\
Angular \\
MongoDB / Mongoose \\
Mocha / Chai / Karma \\
Travis CI \\
HTML / CSS / jQuery \\
Shell  |  LaTeX \\
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\runsubsection{Version Control} \\
\location{}
Git | Github | Mercurial \\
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\runsubsection{Systems} \\
\location{}
Linux Distros: 15 years \\
MacOSX \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}
\runsubsection{Univ of California \\
Los Angeles (UCLA)} \\
\descript{MA History of Science}
\location{Awards and Scholarships}  %throws errors when empty
Chancellor's Prize Fellow \\
History Dept. Fellow \\
EAPSI/JSPS Summer Fellow \\
FLAS Summer \& Annual Fellow \\
\sectionsep
\runsubsection{Univ of California \\
Santa Cruz (UCSC)} \\
\descript{BA in Anthropology}
\location{}
Highest Honors in the Major \\
Highest Honors Senior Thesis \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TECH EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Tech-Education}
\runsubsection{Code Fellows PDX} \\
\descript{Certificate}
\location{}
{\href{https://www.codefellows.org/courses/code-401/advanced-software-development-in-full-stack-javascript/}
{ Advanced Software Dev \\
Full-Stack JavaScript}} \\

\end{minipage} 
\end{document}
\documentclass
